Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Load library and files}
library('dplyr')
library('tidyr')
library('ggplot2')
library('gridExtra')

df_facebook <- read.csv('pseudo_facebook.tsv', sep = '\t')
df_facebook <- tbl_df(df_facebook)
```

```{r Third Qualitative Variable}
p1 <- ggplot(aes(x = gender, y = age),
       data = subset(df_facebook, !is.na(gender))) +
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

p2 <- ggplot(data = subset(df_facebook, !is.na(gender)),
       aes(x = age, y = friend_count)) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
grid.arrange(p1, p2,  ncol = 1)
```

```{r}
fc_by_age_gender <- df_facebook %>%
  filter(!is.na(gender)) %>%
  group_by(age, gender)%>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age, gender)

str(fc_by_age_gender)
```


***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(data = fc_by_age_gender,
       aes(y = median_friend_count, x = age)) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
fc_by_age_gender_wide <- fc_by_age_gender %>%
  select(age, gender, median_friend_count) %>%
  spread(gender, median_friend_count)
```

```{r}
install.packages('reshape2')
library(reshape2)

fc_by_age_gender_wide <- dcast(fc_by_age_gender,
                               age ~ gender,
                               value.var = 'median_friend_count')
```

***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(data = fc_by_age_gender_wide,
       aes(x = age, y = female/male)) +
  geom_line() +
  geom_hline(yintercept = 1, linetype = 3)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
# df_facebook$year_joined <- sapply(df_facebook$tenure, function(x) floor(2014 - x/365))
df_facebook$year_joined <- floor(2014 - df_facebook$tenure/365)

table(df_facebook$year_joined)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
?cut
breaks <- c(2004, 2009, 2011, 2012, 2014)
df_facebook$year_joined_bucket <- cut(df_facebook$year_joined, breaks = breaks)
table(df_facebook$year_joined_bucket, useNA = 'ifany')
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(data = subset(df_facebook, !is.na(year_joined_bucket)),
       aes(x = age, y = friend_count)) +
  geom_line(aes(color = year_joined_bucket), stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(data = subset(df_facebook, !is.na(year_joined_bucket)),
       aes(x = age, y = friend_count)) +
  geom_line(aes(color = year_joined_bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
# df_facebook %>%
#   filter(tenure > 0) %>%
#   summarise(max_friend_rate = max(friend_count / tenure),
#             median_friend_rate = median(friend_count / tenure))

with(subset(df_facebook, tenure > 0), summary(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate? .2205

What is the maximum friend rate? 417

```{r Friendships Initiated}

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

