Lesson 3
========================================================

***

### What to Do First?
**Notes:** Verificar a pasta que se encontra, caso necessário trocar a pasta e listar os arquivos.

```{r Show directory and change location if necessary}
getwd()
list.files()
```

***

### Pseudo-Facebook User Data
**Notes:** Carregar os dados em uma variável.

```{r Pseudo-Facebook User Data}
df <- read.delim('pseudo_facebook.tsv')
head(df)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```

***

#### What are some things that you notice about this histogram?
**Response:** O dia primeiro existem muito mais aniversários do que demais dias, e o dia 31 existem muito menos. Erá esperado que estivesse mais próximos todos os valores.

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
**Response:** A foto de um lanche artesanal que fizemos entre amigos.

#### How many of your friends do you think saw that post?
**Response:** 10

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
**Response:** 60%

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting, fig.align='center', fig.width=15, fig.height=15}
ggplot(data=df, aes(x=dob_day)) +
  geom_histogram() +
  scale_x_continuous(breaks=1:31) +
  facet_wrap(~dob_month, ncol=3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
# qplot(data=df, x=friend_count)
ggplot(aes(x=friend_count), data=df) +
  geom_histogram()
```

#### How is this plot similar to Moira's first plot?
**Response:** Existe uma grande quantidade de pessoas com poucos amigos sendo a maioria com zero amigos.

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
# qplot(x = friend_count, data = df, xlim = c(1,1000)) + labs(y = 'count')
ggplot(aes(x = friend_count), data = df) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(1,1000))
```

### Exploring with Bin Width
**Notes:** A grande maioria dos valores escolhidos eram entre 20, 50 e 100

***

### Adjusting the Bin Width
Notes:

```{r}
ggplot(aes(x=friend_count), data=df) +
  geom_histogram(binwidth=50) +
  scale_x_continuous(limits=c(1,1000), breaks=seq(0,1000,50))
```


### Faceting Friend Count
```{r Faceting Friend Count, fig.align='center', fig.asp=.30, fig.width=15}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
# qplot(x = friend_count, data = df, binwidth = 50) +
#   scale_x_continuous(limits = c(0, 1000),
#                      breaks = seq(0, 1000, 50)) +
#   facet_grid(~gender)
ggplot(aes(x = friend_count), data = df) +
  geom_histogram(binwidth = 50) +
  scale_x_continuous(limits = c(1,1000),
                     breaks = seq(0,1000,50)) +
  facet_grid(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values, fig.height = 10, fig.width = 15, fig.asp = .30, fig.align = "center"}
ggplot(aes(x = friend_count), data = subset(df, !is.na(gender))) +
  geom_histogram(binwidth = 50) +
  scale_x_continuous(limits = c(1, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_grid(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(df$gender)
by(df$friend_count, df$gender, summary)
```
```{r}
fq <- by(df$friend_count, df$gender, summary)
round(fq$female[3]) -  round(fq$male[3])
```


#### Who on average has more friends: men or women?
**Response:** Mulheres em média tem mais amigos.

#### What's the difference between the median friend count for women and men?
**Response:** 22

#### Why would the median be a better measure than the mean?
**Response:** A mediana é um valor mais robusto, como os grupos tem quantidades diferentes, uma contagem maior de usuários pode modificar a média de amigos.

***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x = tenure), data = df) +
  geom_histogram(color = 'black', fill = 'orange')
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x = tenure/365), data = df) +
  geom_histogram(binwidth = .25, color = 'black', fill = 'orange') +
  scale_x_continuous(limits = c(0, 7),
                     breaks = seq(0, 7, 1))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure/365), data = df) +
  geom_histogram(binwidth = .25, color = 'black', fill = 'orange') + 
  scale_x_continuous(limits = c(0, 7),
                     breaks = seq(0, 7, 1)) +
  ylab('Number of users in sample') +
  xlab('Number of years using facebook')
```

***

### User Ages
Notes:

```{r}
summary(df$age)
```


```{r User Ages}
ggplot(aes(x = age), data = df) +
  geom_histogram(binwidth = 1, color = 'black', fill = 'orange') +
  scale_x_continuous(limits = c(13, 113),
                     breaks = seq(13, 113, 5)) +
  xlab('Idade dos usuários do Facebook') +
  ylab('Contagem de individuos do Facebook')
```

#### What do you notice?
**Response:** Não existem contagem de pessoas a baixo dos 13 anos e existe contagens altas de pessoas com idades avançadas o que informa outliers além de outros picos.

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

```{r}
install.packages("gridExtra")
library(gridExtra)
```


```{r Friends count using original log10 and sqrt, fig.align='center', fig.asp=.50, fig.width=15, fig.height=15}
p1 <- ggplot(aes(x = friend_count), data = df) +
  geom_histogram(binwidth = 30, color = 'black', fill = 'blue') +
  scale_x_continuous(limits = c(1, 1000),
                     breaks = seq(0, 1000, 100)) +
  ylab('Count facebook users') +
  xlab('Friends normal count')

# Log_10
df$log_fc <- log10(df$friend_count + 1)
summary(df$log_fc)

p2 <- ggplot(aes(x = log_fc), data = df) +
  geom_histogram(binwidth = .25, color = 'black', fill = 'green') +
  scale_x_continuous(limits = c(0, 4),
                     breaks = seq(0, 4, 0.5)) +
  ylab('') +
  xlab('Friends log_10 count')

df <- subset(df, select = -log_fc)

# SQRT
df$sqr_fc <- sqrt(df$friend_count)
summary(df$sqr_fc)
p3 <- ggplot(aes(x = sqr_fc), data = df) +
  geom_histogram(binwidth = 1, color = 'black', fill = 'red') +
  scale_x_continuous(limits = c(0, 71),
                     breaks = seq(0, 71, 5)) +
  ylab('') +
  xlab('Friends sqrt count')

df <- subset(df, select = -sqr_fc)

grid.arrange(p1, p2, p3, ncol = 3)
```


```{r Friends count using original log10 and sqrt 2, fig.align='center', fig.asp=.50, fig.width=15, fig.height=15}
p1 <- ggplot(aes(x = friend_count), data = df) +
  geom_histogram(binwidth = 30, color = 'black', fill = 'blue') +
  ylab('Count facebook users') +
  xlab('Friends normal count')

# Log_10
p2 <- ggplot(aes(x = log10(friend_count)), data = df) +
  geom_histogram(binwidth = .25, color = 'black', fill = 'green') +
  ylab('') +
  xlab('Friends log_10 count')

# SQRT
p3 <- ggplot(aes(x = sqrt(friend_count)), data = df) +
  geom_histogram(binwidth = 1, color = 'black', fill = 'red') +
  ylab('') +
  xlab('Friends sqrt count')

grid.arrange(p1, p2, p3, ncol = 3)
```

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
p1 <- ggplot(aes(x = friend_count), data = df) + geom_histogram()
p2 <- p1 + scale_x_log10()
p3 <- p1 + scale_x_sqrt()
grid.arrange(p1, p2, p3, ncol=1)
```

***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = www_likes, y = ..density..), data = subset(df, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) +
  scale_x_continuous() +
  scale_x_log10() +
  xlab('Like counts') +
  ylab('Percentage of users with that like counts')
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(df$www_likes, df$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
ggplot(aes(x = gender, y = friend_count),
       data = subset(df, !is.na(gender))) +
  geom_boxplot() +
  coord_cartesian()
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
ggplot(aes(x = gender, y = friend_count),
       data = subset(df, !is.na(gender))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
ggplot(aes(x = gender, y = friendships_initiated),
       data = subset(df, !is.na(gender))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 150))
```

#### On average, who initiated more friendships in our sample: men or women?
**Response:** Mulheres
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
by(df$friendships_initiated, df$gender, summary)
```

**Response:** Se olharmos para a mediana ou para o primeiro e terceiro quartil verificamos que mulheres tem um maior número de pedidos.

***

### Getting Logical
Notes:

```{r Getting Logical}
summary(df$mobile_likes)
summary(df$mobile_likes > 0)
df$mobile_check_in <- NA
df$mobile_check_in <- ifelse(df$mobile_likes > 0, 1, 0)
df$mobile_check_in <- factor(df$mobile_check_in)
round(summary(df$mobile_check_in) / length(df$mobile_check_in) * 100)
```

**Response:** 65%

***

### Analyzing One Variable
**Reflection:** Aprendi a utilizar várias funcionalidades da linguagem R e a trabalhar com o rstudio, também aprendi a fazer analises usando ggplot, analisando valores de variáveis e dividindo em grupos distintos. Também aprendi a modificar o gráfico de forma que a resposta seja visualmente mais compreensível. 

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!